API design for machine learning: experiences from scikit-learn

### 2014-02-12 paper.tex
change my affiliation (again)
stress composition and model selection in the introduction

\affil[1]{ISLA, University of Amsterdam}
\affil[2]{University of Liège}
\affil[3]{Kobe University}
\affil[4]{Parietal, INRIA Saclay}
\affil[5]{University of Bonn}
\affil[6]{University of Bucharest}
\affil[7]{Ciuvo GmbH}
\affil[8]{Institut Mines-Telecom, Telecom ParisTech, CNRS LTCI}
\affil[9]{University of Ballarat}
\affil[10]{University of Washington}
\affil[11]{Samsung Electronics Research Institute}

@@

\citet{pedregosa2011} briefly presented \sklearn and
benchmarked it against several competitors.
In this paper, we present an
in-depth analysis of design choices made when building the library,
detailing how we organized and operationalized
common machine learning concepts.
We first present in section~\ref{sec:core-api} the central application
programming interface (API) and then describe, in section~\ref{sec:advanced-api},
advanced API mechanisms built on the core interface.
Section~\ref{sec:implementation} briefly describes the implementation.
Section~\ref{sec:comparison} then
compares \sklearn to other major projects in terms of API\@.
Section~\ref{sec:future_work} outlines some of the objectives for
a \sklearn 1.0 release.
We conclude by summarizing the major points of this paper in
section~\ref{sec:conclusions}.

>>>>

\affil[1]{ISLA, University of Amsterdam; Netherlands eScience Center}
\affil[2]{University of Liège}
\affil[3]{Kobe University}
\affil[4]{Parietal, INRIA Saclay}
\affil[5]{University of Bonn}
\affil[6]{University of Bucharest}
\affil[7]{Ciuvo GmbH}
\affil[8]{Institut Mines-Telecom, Telecom ParisTech, CNRS LTCI}
\affil[9]{University of Ballarat}
\affil[10]{University of Washington}
\affil[11]{Samsung Electronics Research Institute}

@@

\citet{pedregosa2011} briefly presented \sklearn and
benchmarked it against several competitors.
In this paper, we present an
in-depth analysis of design choices made when building the library,
detailing how we organized and operationalized
common machine learning concepts.
We first present in section~\ref{sec:core-api}
the central concepts of our application programming interface (API).
In section~\ref{sec:advanced-api}, we discuss
advanced API mechanisms built on the core interface,
focusing on composition of operations
and on the important problem of model selection.
Section~\ref{sec:implementation} briefly describes the implementation.
Section~\ref{sec:comparison} then
compares \sklearn to other major projects in terms of API\@.
Section~\ref{sec:future_work} outlines some of the objectives for
a \sklearn 1.0 release.
We conclude by summarizing the major points of this paper in
section~\ref{sec:conclusions}.
